Separating Use and Reuse to Improve Both

### 2017-05-20 FACS/RelatedWork.tex
.

@@

Our idea of fully separate inheritance and subtyping has some precedence
In all the line of work of Ferruccio [cite many] neither traits nor classes introduce nominal types,
that are provided only by interfaces.
In DeepFjig[] classes introduce nominal types but in an innatural way, the type of \Q@this@ is only \Q@This@ (sometimes called \Q@<>@) and not the nominal type of its class.

@@

Our compilation model is a clear step forward with respect to 
\cite[metaFjig, deepFjig,myThesis], where all code was required to declare all the abstract dependencies all of the time.

>>>>

\section{Extensions and practical experience}
The model presented here is very easy to extend:
For example nested classes can be easly added,giving us enough power to easly solve the expression problem as in \cite{deepfjig}. More composition operators can be added in addition to use. Indeed
we just need to be sure that every newly added operator respects the following criteria:

\begin{itemize}
\item As for \use, the operato does not need to be total, but if it fails it needs to provide an error that will be reported to the programmer.
\item When the operator takes in input only traits (they are going to be well typed), if a result is produced,
 such result is well typed.
\item When the operator takes in input also code literal, if a non well typed result is produced,
the type error must be tracked back to code in one of those non typed yet code literals.
 \end{itemize}
 That is, our model can easly support all the operators of \cite{deep}.

 Our simplified model represent the conceptual core of  a novel programming language (http://L42.is)
 we are currently working at.
 L42 contains the extensions described before and much more, and provide a concrete example of the usability of our model.

 The main difference is that code literal are first class values in L42, thus we do not need traits as a language concept, but just as a method returning such code literal.

@@

Our idea of fully separate inheritance and subtyping has some precedence
In all the line of work of Ferruccio [cite many] neither traits nor classes introduce nominal types,
that are provided only by interfaces.
In DeepFjig[] classes introduce nominal types but in an innatural way, the type of \Q@this@ is only \Q@This@ (sometimes called \Q@<>@) and not the nominal type of its class: that is in DeepFjig 
\Q@A:{ method A m()this}@ is not well typed.

@@

Our compilation model is a clear step forward with respect to 
\cite[metaFjig, deepFjig,myThesis,allferruccioWorkBefore2017], where all code was required to declare all the abstract dependencies all of the time.
